Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
comment out chunks not to run

plot_grid(p1, p2)
```
```{r}
s.df <- df %>% drop_na(s.id) %>%
  group_by(indiv) %>%
  sample_n(., 50)

@@

for(i in 1:individual){
  dat <- s.df %>% 
    filter(indiv == i)
  #g <- fitdist(dat$disp, distr = "weibull", method = 'mle', lower = c(0,0))
  g <- fitdistr(dat$disp, densfun = "weibull", lower = c(0,0))
  prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
                          est.scale = as.numeric(g$estimate[2]),
                          loglik = g$loglik, indiv = i)
  weib.fits <- rbind.data.frame(weib.fits, prms.weib)
  # plot(g)
}

>>>>

plot_grid(p1, p2)
```
```{r eval=FALSE}
# Sample once for estimating parameters
s.df <- df %>% drop_na(s.id) %>%
  group_by(indiv) %>%
  sample_n(., 50)

@@

for(i in 1:n.individuals){
  dat <- s.df %>% 
    filter(indiv == i)
  #g <- fitdist(dat$disp, distr = "weibull", method = 'mle', lower = c(0,0))
  g <- fitdistr(dat$disp, densfun = "weibull", lower = c(0,0))
  prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
                          est.scale = as.numeric(g$estimate[2]),
                          loglik = g$loglik, indiv = i)
  weib.fits <- rbind.data.frame(weib.fits, prms.weib)
  # plot(g)
}
